Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-18 doc/GMP2015/s08_pinnedline.tex

The optimal qusecs DR-plan can also be applied to analyze and solve
the structure of  cross-linking microfibrils in collagen and cellulose in biology,
by modeling these structures as {\em pinned line-incidence systems}.

{\em Collagen} is an important protein material in biological tissues with highly elastic mechanical property.
{\em Cellulose} is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}).
Both of these substances consist of a large number {\em microfibrils},
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally
each of which is cross-linked at 2 places with some two other fibrils,
where the {\em  cross-linking} is like an incidence constraint that
the two crosslinked fibrils can slide with each other  \cite{xxx} (see Figure~\ref{fig:crosslink}).

@@

\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
  \caption{}
  \label{fig:cellulose}
\end{subfigure}
\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=\linewidth]{img/crosslink}
  \caption{}
  \label{fig:crosslink}
\end{subfigure}%
\caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface~\cite{xxx}. (b) Cross-linking of cellulose microfibrils~\cite{xxx}.}
\end{figure}

@@

The cross-linking  microfibrils can be modeled as a pinned line-incidence constraint system in $\mathbb{R}^2$,
where incidence constraints are used instead of distance constraints.

A {\em pinned line-incidence system} $(G,\delta)$  
is a graph $G=(V,E)$ together with parameters $\delta$ specifying $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$, 
such that each edge is constrained to lie on a line passing through 
the corresponding pin, i.e.\ $\delta: E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$  
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$  \cite{xxx}. Note that no trivial motion exists since the pins have fixed positions on the plane.
In particular, both a single vertex and a single edge are under-constrained graphs.
%and the smallest over-constrained graph has $6$ vertices.

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs, 
{\em a well-constrained pinned line-incidence graph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs. 
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. 
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We define a {\em trivial} graph to be a single vertex and make the following modification to the definition of the DR-plan:

@@

\begin{definition}

 The {\em DR-plan} of  a well-constrained pinned line-incidence graph $G$ is one in which 
(1) each child node of a non-leaf node $C$ is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$, and
(2) a leaf node is a single edge.
 % Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}
\end{definition}

@@

\begin{corollary}
Given a well-constrained  pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\label{cor:pinned}
\end{corollary}

The following lemma serves a similar function to Lemma~\ref{lemma:union_intersection} in Section~\ref{sec:union_intersection}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
and can be proved using a similar counting based argument.

\begin{lemma}
\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$,
where each of them can be either  a single edge or a connected well-constrained subgraph.
There are only two possible cases:
\begin{itemize}
\item At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is trivial.
\item Both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained.
\end{itemize}
%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}
\end{lemma}

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs 
is given in Appendix~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}

@@

\noindent {\bf Note:} The recombination problem for  pinned line-incidence systems is trivial.
Since the pins are given fixed positions in the plane,
 the solutions of a well-constrained sub-system will automatically be consistent with solutions of the remaining of the system.

>>>>

The optimal qusecs DR-plan can also be applied to analyze and solve
the structure of  cross-linking microfibrils in collagen and cellulose
in biology, by modeling these structures as \dfn{pinned line-incidence
systems}.

\dfn{Collagen} is an important protein material in biological tissues with highly elastic mechanical property.
\dfn{Cellulose} is the most important constituent of the cell wall of plants (see Figure~\ref{fig:cellulose}).
Both of these substances consist of a large number \dfn{microfibrils},
%fibril itself straight?
%Each fibril is attached to some fixed larger organelle/membrane at one spot (typically on the boundary).
%It is additionally
each of which is cross-linked at 2 places with some two other fibrils,
where the \dfn{cross-linking} is like an incidence constraint that the
two crosslinked fibrils can slide with each other  \uncited (see
Figure~\ref{fig:crosslink}).

@@

\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=.8\linewidth]{img/AFM_Innventia_nanocellulose}
  \caption{}
  \label{fig:cellulose}
\end{subfigure}
\begin{subfigure}{.49\linewidth}
  \centering
  \includegraphics[width=\linewidth]{img/crosslink}
  \caption{}
  \label{fig:crosslink}
\end{subfigure}%
\caption{(a) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \uncited. (b) Cross-linking of cellulose microfibrils \uncited.}
\end{figure}

@@

The cross-linking microfibrils can be modeled as a pinned line-
incidence constraint system in $\mathbb{R}^2$, where incidence
constraints are used instead of distance constraints.

A \dfn{pinned line-incidence system} $(G,\delta)$ is a graph $G=(V,E)$
together with parameters $\delta$ specifying $|E|$ \textbf{pins} with
fixed positions in $\mathbb{R}^2$, such that each edge is constrained
to lie on a line passing through the corresponding pin, i.e.\ $\delta:
E \rightarrow \mathbb{R}^2$.
%
% $G=(V,E, w_V, w_E)$
%%is a \textbf{2-dimensional pinned line-incidence graph},
% has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
%Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
%such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
%for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
%such that $e$ is constrained to lie on a line passing through $x$.
%%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$
%
A pinned line-incidence graph $G$ is rigid if $|E| = 2|V|$ and $|E'| \le 2|V'|$ for every induced subgraph $(V',E')$ \uncited. Note that no trivial motion exists since the pins have fixed positions on the plane.
In particular, both a single vertex and a single edge are under-constrained graphs.
%and the smallest over-constrained graph has $6$ vertices.

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for pinned line-incidence graphs.
First, we note that %unlike bar-joint graphs,
\vemph{a well-constrained pinned line-incidence graph can be disconnected},
being the disjoint union of two or more well-constrained subgraphs.
This is because the pins have fixed positions on the plane.
%
%the following difference of pinned line-incidence graphs from the bar-joint graphs.
%
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs.
%
%\begin{itemize}
%
%\item For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%no trivial motion exists, therefore {\em no trivial over-constrained graphs exist} (the smallest over-constrained graph has $6$ vertices).\\
%In particular, note that both a single vertex and a single edge are under-constrained graphs.
%
%\item
%For pinned line-incidence graphs,
%since the pins have fixed positions on the plane,
%{\em a well-constrained vertex-maximal proper subgraph can be disconnected},
%being the disjoint union of two or more well-constrained subgraphs. \\
%%Without loss of generality,
%%we slightly modify the requirement of DR-plan for pinned line-incidence graphs
%%such that only connected subgraphs can be considered as a node of the DR-plan.
%
%\end{itemize}
%
We define a \dfn{trivial} graph to be a single vertex and make the following modification to the definition of the DR-plan:

@@

\begin{definition}
The \dfn{DR-plan} of a well-constrained pinned line-incidence graph $G$ is one in which
(1) each child node of a non-leaf node $C$ is either an edge not contained in any well-constrained proper subgraph of $C$, or a \dfn{connected} well-constrained vertex-maximal proper subgraph of $C$, and
(2) a leaf node is a single edge.
 % Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line-incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
%    \begin{enumerate}
%        %\item The root of the tree `contains' $G$.
%        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
%        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
%        \item[4] A node containing a single edge is a leaf.
%    \end{enumerate}
\end{definition}

@@

\begin{corollary}\label{cor:pinned}
Given a well-constrained pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
\begin{enumerate}
    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
    \item if $C_i \cap C_j$ is well-constrained then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
\end{enumerate}
\end{corollary}

The following lemma serves a similar function to Remark~\ref{lemma:union_intersection} in Section~\ref{sec:union_intersection}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
and can be proved using a similar counting based argument.

\begin{remark}\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$,
where each of them can be either a single edge or a connected well-constrained subgraph.
There are only two possible cases:
(1) At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained.
%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}
\end{remark}

Given Remark~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned
line-incidence graphs is given in Appendix~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}

@@

\noindent
\note The recombination problem for  pinned line-incidence systems is trivial.
Since the pins are given fixed positions in the plane,
the solutions of a well-constrained sub-system will automatically be consistent with solutions of the remaining of the system.

### 2014-12-18 doc/GMP2015/s09_problems.tex

The {\em restricted optimal DR-planning problem} requires
DR-plans of one of these types, which reduces to recognizing if
the input graph is a 2-tree or a tree-decomposable graph for which simple
near-linear time algorithms are available \cite{XX} and the DR-plan is a
by-product output of the recognition algorithm.

In the recombination setting, the corresponding {\em restricted
OMD$_k$  problem}
requires the reduced graph $G'$  and its isostatic completion $H$ to be
2-trees as in Section \ref{2-tree-completion}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{tdecomp}. Clearly these problems have deterministic polynomial time
algorithms, the algorithms run in time exponential in $k$.
As a result, when $k$ is part of the input, the {\em restricted OMD problem}
has the potential to be difficult.
For example,  when the isostatic completion $H$ is required to be a 2-tree
the restricted OMD problem is reducible to the maximum spanning series-parallel
subgraph problem shown by \cite{XX,XX} to be NP-complete
even if the input graph is planar of maximum degree at most 6.
However, since the OMD problem has other input restrictions
such as not having any proper isostatic subgraphs,
it is not clear if the reverse reduction exists and hence it is unclear
whether the OMD problem is NP-complete.
The same holds for the restricted OMD problem where the isostatic completion
$H$ is required to be a tree-decomposable graph of low Cayley complexity (i.e, have
special, small DR-plans).
One potential obstacle to an indecomposable graph $G$'s membership in the
restricted OMD$_k$ for small $k$ is
if $G$ is triconnected and has large girth. In fact,  6-connected (hence
rigid) graphs with
arbitrarily large girth have been constructed in \cite{XX}.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an underconstrained system to an isostatic one with a small
DR-plan.
\begin{observation}
The (decision version of) the {\bf optimal completion problem (OC)} from \cite{bib:survey, j-a,
fang} is OMD$_0$.
\end{observation}.
In fact, a {\em restricted OC} problem was studied by \cite{j-a} requiring the
completion to be tree-decomposable.
It is not clear if the reverse reduction holds, i.e, is OMD reducible to OC?

We now connect the OMD problem to the informal {\em optimal recombination
(OR)} problem
mentioned as motivation at the beginning of
Section \ref{sec:recomb}.

In order to connect the OR problem to OMD,
when the input graph for is the isostatic graph at the DR-plan root, we do not consider the case
where the two child {\em solved subgraphs}
(corresponding to already solved subsystems)
have a nontrivial intersection (in this case
the recombination is trivial). We only consider the case where no two child
solved subgraphs (resp. two root subgraphs when the input graph is
underconstrained) share more than 1 vertex.
We replace such solved subgraphs  by isostatic graphs as
follows. If a solved subgraph shares at most one vertex with the remainder of
the graph, simply replace it by an edge one of whose endpoints  is
the shared vertex. Otherwise, replace it by  a 2-tree graph of the shared vertices.
Finally, we add the additional
restriction to the OM Problem that
when any edge in a solved subgraph is chosen among the $k$ edges to be
removed, in fact the entire solved subgraph must be removed  and all of its
edges must be counted in $k$.

This reduction is used also for transferrring  algorithms for
optimal DR-planning, recombination, completion, OMD, and other problems and
to so-called {\em
multi-body pin} from so-called{\em bar-joint-systems}, by showing that the corresponding
prblems for the latter are reduced to the correspnding problems on
bar-joint systems.

{\bf Note.} This section deals only with bar-joint systems, however,
extensions of several of these problems, approaches and solutions
to other qusecs beyond  bar-joint - specifically pinned line incidence
systems and
multi-body-pin systems
will be expanded in Sections \ref{sec:pinnedline} and \ref{sec:bodypin}.

>>>>

The \dfn{restricted optimal DR-planning problem} requires DR-plans of
one of these types, which reduces to recognizing if the input graph is
a 2-tree or a tree-decomposable graph for which simple near-linear
time algorithms are available \uncited and the DR-plan is a
by-product output of the recognition algorithm.

In the recombination setting, the corresponding \dfn{restricted
OMD$_k$  problem} requires the reduced graph $G'$ and its isostatic
completion $H$ to be 2-trees as in Section \ref{sec:2-tree-reduction}
or to be a low Cayley complexity tree-decomposable graph as in Section
\ref{sec:tdecomp}. Clearly these problems have deterministic
polynomial time algorithms, the algorithms run in time exponential in
$k$. As a result, when $k$ is part of the input, the \dfn{restricted
OMD problem} has the potential to be difficult. For example, when the
isostatic completion $H$ is required to be a 2-tree the restricted OMD
problem is reducible to the maximum spanning series-parallel subgraph
problem shown by \uncited\uncited to be NP-complete even if the input
graph is planar of maximum degree at most 6. However, since the OMD
problem has other input restrictions such as not having any proper
isostatic subgraphs, it is not clear if the reverse reduction exists
and hence it is unclear whether the OMD problem is NP-complete. The
same holds for the restricted OMD problem where the isostatic
completion $H$ is required to be a tree-decomposable graph of low
Cayley complexity (i.e, have special, small DR-plans). One potential
obstacle to an indecomposable graph $G$'s membership in the restricted
OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth.
In fact, 6-connected (hence rigid) graphs with arbitrarily large girth
have been constructed in \uncited.
%
\subsection{Optimal Modification, Completion and Recombination: formal
connections}
%
The OMD problem is closely related to a well-studied problem of
completion of an under-constrained system to an isostatic one with a
small DR-plan.
\begin{observation}
    The (decision version of) the {\bf optimal completion problem
    (OC)} from \cite{bib:survey, j-a, fang} is OMD$_0$.
\end{observation}.
In fact, a \dfn{restricted OC} problem was studied by \cite{j-a}
requiring the completion to be tree-decomposable. It is not clear if
the reverse reduction holds, i.e, is OMD reducible to OC?

We now connect the OMD problem to the informal \dfn{optimal
recombination (OR)} problem mentioned as motivation at the beginning
of Section \ref{sec:recomb}.

In order to connect the OR problem to OMD, when the input graph for is
the isostatic graph at the DR-plan root, we do not consider the case
where the two child \dfn{solved subgraphs} (corresponding to already
solved subsystems) have a nontrivial intersection (in this case the
recombination is trivial). We only consider the case where no two
child solved subgraphs (resp. two root subgraphs when the input graph
is under-constrained) share more than 1 vertex. We replace such solved
subgraphs  by isostatic graphs as follows. If a solved subgraph shares
at most one vertex with the remainder of the graph, simply replace it
by an edge one of whose endpoints  is the shared vertex. Otherwise,
replace it by  a 2-tree graph of the shared vertices. Finally, we add
the additional restriction to the OM Problem that when any edge in a
solved subgraph is chosen among the $k$ edges to be removed, in fact
the entire solved subgraph must be removed  and all of its edges must
be counted in $k$.

This reduction is used also for transferring  algorithms for optimal
DR-planning, recombination, completion, OMD, and other problems and to
so-called \dfn{multi-body pin} from so-called \dfn{bar-joint-systems},
by showing that the corresponding problems for the latter are reduced
to the corresponding problems on bar-joint systems.

\note This section deals only with bar-joint systems, however,
extensions of several of these problems, approaches and solutions to
other qusecs beyond  bar-joint - specifically pinned line incidence
systems and multi-body-pin systems will be expanded in Sections
\ref{sec:pinnedline} and \ref{sec:bodypin}.
